Optimal Finite Element Integration

### 2015-08-07 TOMS_Paper/assembly.tex
Readjust Th discussion

Experiments were run on a single core of an Intel I7-2600 (Sandy Bridge) CPU, running at 3.4GHz, 32KB L1 cache and 256KB L2 cache. The Intel Turbo Boost and Intel Speed Step technologies were disabled. The Intel \texttt{icc 15.2} compiler was used. The compilation flags used were \texttt{-O3, -xHost, -ip}, which can trigger \texttt{AVX} autovectorization.

@@

With respect to the memory constraint $C_2$ introduced in Section~\ref{sec:mem-const}, since we are running sequential programs we set $T_H = LLC_{size}$; that is, the amount of space that temporaries due to pre-evaluation can occupy is bounded by the size of the processor L3 cache. If, on the other hand, a parallel program were run, then a more sensible value for $T_H$ would be the size of the last level of private cache (L2, on our Sandy Bridge machine); this would avoid cache misses and memory conflicts and, therefore, potential drops in runtime.

@@

\paragraph{Elasticity}
The performance results for the elastic model are displayed in Figure~\ref{fig:elasticity}. We note how the fact that \texttt{auto} opts for \texttt{tens} when $nf=1$ leads, generally, to sub-optimal execution times. This is different than in the case of the Helmholtz equation, in which \texttt{tens} (and, generally, pre-evaluation through \texttt{cfO2}), tends to be the best alternative when a single coefficient is present. With $q=4$, pre-evaluation is triggered in \texttt{cfO2} when $nf0$. When $nf=1$, pre-evaluation is found profitable in terms of operation count, although it is not performed because of exceeding the working set threshold $T_H$ imposed by memory constraint $C_2$. We have tried running the same experiments with $T_H = \infty$ and noticed a significant drop in runtime for all values of $p$ (\texttt{cfO2} was generally slower than \texttt{cfO1}). This confirms the importance of memory constraints.

>>>>

Experiments were run on a single core of an Intel I7-2600 (Sandy Bridge) CPU, running at 3.4GHz, 32KB L1 cache (private), 256KB L2 cache (private) and 8MB L3 cache (shared). The Intel Turbo Boost and Intel Speed Step technologies were disabled. The Intel \texttt{icc 15.2} compiler was used. The compilation flags used were \texttt{-O3, -xHost, -ip}, which can trigger \texttt{AVX} autovectorization.

@@

For what concerns the memory constraint $C_2$ introduced in Section~\ref{sec:mem-const}, we set $T_H = L2_{size}$; that is, the amount of space that temporaries due to pre-evaluation can occupy is bounded by the size of the processor L2 cache (the last level of private cache). For the test cases in which $T_H$ was determinant to prevent pre-evaluation, we also repeated the experiments setting $T_H = L3_{size}$ and $T_H = \infty$. Results of these trials are discussed below.

@@

\paragraph{Elasticity}
The performance results for the elastic model are displayed in Figure~\ref{fig:elasticity}. The fact that \texttt{auto} opts for \texttt{tens} when $nf=1$ leads, generally, to sub-optimal execution times. This is different than in the case of the Helmholtz equation, in which \texttt{tens} (and, generally, pre-evaluation through \texttt{cfO2}), tends to be the best alternative when a single coefficient is present. With $q=4$ and $nf \in [0, 1]$, pre-evaluation in \texttt{cfO2} is found profitable in terms of operation count, although it is not triggered because of exceeding the working set threshold $T_H$. Running the same experiments with $T_H = \infty$ resulted in significant runtime increases for all values of $p$. Running the same experiments with $T_H = L3_{size}$ resulted in a considerable improvement for $nf = 0$, with \texttt{cfO2} becoming the fastest alternative. Our explanation for this is that by running a sequential program, a process has exclusive access to the memory bandwidth of the system, so pre-fetching minimizes cache misses without hurting concurrent processes (since there are none).
